My wonderful paper

### 2024-10-31 _manuscript/_tex/index.tex
add dot points

@@

@@

@@

@@

\begin{itemize}
\item
  how to systematically simulate data is still unknown, sensitivity of
  the simulation to the resutls
\item
  currently no automated way to generate unit tests
\end{itemize}

>>>>

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{3}
\tableofcontents
}

\newpage

@@

\section{Literature review}\label{literature-review}

\subsection{Diagnosing unexpected outcomes in data
analysis}\label{diagnosing-unexpected-outcomes-in-data-analysis}

\subsection{Unit tests}\label{unit-tests}

\subsection{Data quality checks}\label{data-quality-checks}

@@

\subsection{Framing checks into unit
tests}\label{framing-checks-into-unit-tests}

@@

\subsection{A workflow to assess the quality of unit
tests}\label{a-workflow-to-assess-the-quality-of-unit-tests}

@@

\begin{itemize}
\item
  how to systematically simulate data is still unknown, sensitivity of
  the simulation to the results
\item
  plotting is a critical way to check data and they can still be frame
  into a unit test. it is a open problem to how to encode the
  visualization into the unit tests. Maybe a procedure like confirm plot
  (this looks alright to you) and then press the button to continue
\item
  currently no automated way to generate unit tests
\end{itemize}

### 2024-10-31 index.qmd
add dot points

---
title: "My wonderful paper"
abstract: "This is the abstract"
cite-method: natbib
bibliography: references.bib
documentclass: jds
format:
  pdf:
   keep-tex: true
preamble: >
  \usepackage{amsfonts,amsmath,amssymb,amsthm}
editor_options: 
  chunk_output_type: console
---

@@

@@

@@

@@

@@

* how to systematically simulate data is still unknown, sensitivity of the simulation to the resutls

>>>>

---
title: "My wonderful paper"
abstract: "This is the abstract"
cite-method: natbib
bibliography: references.bib
documentclass: jds
format:
  pdf:
   keep-tex: true
   toc: true
preamble: >
  \usepackage{amsfonts,amsmath,amssymb,amsthm}
editor_options: 
  chunk_output_type: console
---

@@

\newpage

@@

# Literature review

## Diagnosing unexpected outcomes in data analysis

## Unit tests

## Data quality checks

@@

## Framing checks into unit tests

@@

## A workflow to assess the quality of unit tests

@@

* how to systematically simulate data is still unknown, sensitivity of the simulation to the results

* plotting is a critical way to check data and they can still be frame into a unit test. it is a open problem to how to encode the visualization into the unit tests. Maybe a procedure like confirm plot (this looks alright to you) and then press the button to continue
